### 2023-05-24 doc/SAP/sap.tex

\begin{enumerate}
    \item The number of positive bioaerosol and saliva samples.
    \item Viral load concentration in positive bioaerosol and saliva samples.
    \item The aerosol/particle number, and matter mass concentrations.
    \item The number of coughs.
\end{enumerate}

@@

\subsubsection{Viral load concentration in positive samples}\label{subsubsec:viral_load}

Molecular analysis will determine the viral load concentration in positive samples. The viral load concentration in positive samples will be analyzed with a hierarchical linear regression model 
\begin{align*}
    y | \beta_0, \beta_1 &\sim \text{Normal}(\mu,s_{y}) \\
    \mu &= \beta_{0[p]} + \beta_{1[p]} \cdot \text{AirCleaner} \\
    \beta_0 &\sim \text{Normal}(\kappa_0, \tau_0) \\
    \beta_1 &\sim \text{Normal}(\kappa_1, \tau_1) \\
    \kappa_0 &\sim \text{Student-t}_5(\mu_{y}, 2.5s_{y}) \\
    \kappa_1 &\sim \text{Student-t}_5\left(0, 2.5\frac{s_{y}}{s_{x}}\right) \\
    \tau_0, \tau_1 &\sim \text{Half-Student-t}_5(0,1) \\
    \sigma &\sim \text{Exponential}\left(\frac{1}{s_{y}}\right),
\end{align*}
where $\mu_{y}$ and $s_{y}$ are the empirical mean and standard deviation of the outcome.

>>>>

\begin{enumerate}
    \item The number of positive bioaerosol and saliva samples.
    \item Viral load concentration in bioaerosol samples.
    \item The aerosol/particle number, and matter mass concentrations.
    \item The number of coughs.
\end{enumerate}

@@

\subsubsection{Viral load concentration in bioaerosol samples}\label{subsubsec:viral_load}

Molecular analysis will determine the viral load concentration in bioaerosol samples, which will be analyzed with a hierarchical linear regression model 
\begin{align*}
    y | \beta_0, \beta_1 &\sim \text{Normal}(\mu,s_{y}) \\
    \mu &= \beta_{0[p]} + \beta_{1[p]} \cdot \text{AirCleaner} \\
    \beta_0 &\sim \text{Normal}(\kappa_0, \tau_0) \\
    \beta_1 &\sim \text{Normal}(\kappa_1, \tau_1) \\
    \kappa_0 &\sim \text{Student-t}_5(\mu_{y}, 2.5s_{y}) \\
    \kappa_1 &\sim \text{Student-t}_5\left(0, 2.5\frac{s_{y}}{s_{x}}\right) \\
    \tau_0, \tau_1 &\sim \text{Half-Student-t}_5(0,1) \\
    \sigma &\sim \text{Exponential}\left(\frac{1}{s_{y}}\right),
\end{align*}
where $\mu_{y}$ and $s_{y}$ are the empirical mean and standard deviation of the outcome.
